Windowed Developer Topic Analysis

### 2009-03-13 lda-paper.tex
more lda paper changes abstract

  At different times, developers focus on different topics and tasks
  during development.  These different topics and times of focus might
  be obvious to developers familar with the project, but other
  stakeholders, like managers, might be less aware of the topics of
  development. Imagine the scenario where developers had to deal with
  issues orthogonal to the features suggested, at the end of the
  iteration a manager would wonder where all the time went, the
  developers might have just blocked all sides issues in with features
  they were initially working on, they might not have noticed their
  focus had changed.  Currently it is difficult for stakeholders to
  audit what actually occurred and when certain features or topics
  were focussed on. We propose and provide a visualization of the
  changing development topics over time. Using

>>>>

  At different times, developers focus on different topics and tasks
  during development.  These different topics and times of focus might
  be obvious to developers familar with the project, but other
  stakeholders, like managers, might be less aware of the topics of
  development. Imagine the scenario where developers had to deal with
  issues orthogonal to the features suggested, at the end of the
  iteration a manager would wonder where all the time went, the
  developers might have just blocked all sides issues in with features
  they were initially working on, they might not have noticed their
  focus had changed.  Currently it is difficult for stakeholders to
  audit what actually occurred and when certain features or topics
  were focussed on. We propose and provide a visualization of the
  changing development topics over time. Our approach takes a topic
  analysis tool like Latent Dirichlet Allocation (LDA) or Latent
  Semantic Indexing (LSI) and instead of applying the tool to the
  entire corpus we apply to windows of the corpus. This allows us to
  see the unique topics of development occuring during a particular
  time period and then see if these individual topics ever reappear.
